Laplacian envelope

### 2015-07-14 Notes/laplace.tex
hessian

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{ideal}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}

@@

Using the exact same proof as in the case $s=0$, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptb_{ij}(s)\eq_j
\end{equation}
%
is independent of the starting state $i$, but now $\eta(s) = \tr\fund(s) - \frac{\tau}{1+s\tau}$.
We can the define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptb_{ij}(s)\eq_j \prn{\frac{1\pm\w_j}{2}} =  \sum_{j\in\pm} \fptb_{ij}(s)\eq_j.
\end{equation}
%
We can arrange the states in order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \eta^w_i(s) = \sum_j \fptb_{ij}(s)\eq_j \w
    = \eta^+_i(s) - \eta^-_i(s) =2\eta^+_i(s) - \eta(s) =\eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing $\eta^w_i(s)$ is the same as the order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
These quantities can still be used when $\w$ takes more than two values.

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurvehom} (ignoring the denominator)
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) \\
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }{ \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s - r\frg}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \enc_{ij} (\eta^w_{i}(s) - \eta^w_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

In analogy with the case $s=0$, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    c_k(s) &= \sum_{ij} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \\
    a_i(s) &= \sum_j \eq_i \enc_{ij} (\eta^w_{i}(s) - \eta^w_{j}(s)),\\
    \implies
    \hat{A}(s) &= \sum_k c_k(s) \eq_k \w_k
      = \sum_i a_i(s).
  \end{aligned}
\end{equation}
%

@@

Using the same approach as the area bound in \cite{Lahiri2013synapse}, and defining $\theta_i(s) = \sum_j \fptb_{ij}(0) a_j(s)$,  we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
  \pdiff{\hat{A}(s)}{\Mh\potdep_{mn}}
     = f\potdep \eq_m \prn{ r \brk{\theta_m(s) - \theta_n(s)}
     +\prn{rc_m(s) \pm 1} \brk{\eta^w_m(s) - \eta^w_n(s)} },
\end{equation}
%
with the upper/lower sign in $\pm$ corresponding to derivatives \wrt $\M\potdep$.
The term with $\Theta(s)$ comes from differentiating $\eq$, the term with $c(s)$ comes from differentiating $\eta^w(s)$ and the term with $\pm1$ comes from differentiating $\enc$ in \eqref{eq:larea}.

@@

Now we'll maximise $\snrb(\tau)$ for some fixed $\tau$, subject to the constraints \eqref{eq:constr}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding $\eq\w$ fixed.
We can maximise the ration \wrt $\eq\w$ later.
Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eq_i \enc_{ij} (\eta^w_i(s) - \eta^w_j(s))
        +\sum_{i j} \prn{ f\pot\mu\pot_{ij} \M\pot_{ij} + f\dep\mu\dep_{ij} \M\dep_{ij} }\\
        &+ \lambda \prn{ \Delta\pr - \sum_i \eq_i\w_i },
\end{aligned}
\end{equation}
%
where $\Delta\pr$ is the constant value we are holding $\eq\w$ at.
After maximising
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\M\potdep_{ij}} = 0, \quad
  \mu\potdep_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu\potdep_{ij}} \geq 0, \quad
  \mu\potdep_{ij}\pdiff{\CL}{\mu\potdep_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
The derivatives, for $m \neq n$ are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{f\potdep} \pdiff{\CL}{\Mh\potdep_{mn}} =& \,
      \eq_m \prn{ r \brk{\theta_m(s) - \theta_n(s)}
     +\prn{rc_m(s) \pm 1} \brk{\eta^w_m(s) - \eta^w_n(s)} } \\
     &+ \mu\potdep_{mn} -  \mu\potdep_{mm}
     + \lambda \eq_m \sum_i (\fptb_{mi}(0)-\fptb_{ni}(0)) \eq_i\w_i.
\end{aligned}
\end{equation}
%
These have the same form as for $s=0$, which allowed us to argue that the model with maximal area must have the serial topology, \cite{Leibold2008serial,Ben-DayanRubin2007sparse}.

@@

Here we will look at the model in \autoref{fig:heuristicmodels}\ref{fig:serial_uniform}.
Looking at \eqref{eq:larea}, the only thing we need is differences in $\eta^w_i(s)$.
In fact, given that the only nonzero elements of $\enc$ are
%
\begin{equation}\label{eq:unienc}
  \enc_{ii+1}=\frac{1}{2} \quad\text{for}\quad i<M,
  \qquad
  \enc_{ii-1}=-\frac{1}{2} \quad\text{for}\quad i>1,
\end{equation}
%
and $\eq_i = \frac{1}{M}$, we have
%
\begin{equation}\label{eq:uniareaeta}
  \hat{A}(s) = \frac{\eta^w_1(s) - \eta^w_M(s)}{M}.
\end{equation}
%

Note that
%
\begin{equation}\label{eq:etafund}
  \eta^w(s) = \text{const.} - \fund(s)\w.
\end{equation}
%
As we are only interested in differences of the $\eta^w_i(s)$, we can drop the constant.
Then
%
\begin{equation}\label{eq:etarecur}
  -(s\I + \onev\pib - \frg)\eta^w(s) = \w.
\end{equation}
%
We can then write
%
\begin{equation}\label{eq:detarecur}
  \eta^w(s) = -\frac{(\pib\eta^w(s))\onev+\w}{s} + \delta\eta(s),
  \qquad
  (\frg-s\I)\delta\eta(s) = \frac{\frg\w}{s}.
\end{equation}
%
As we are only interested in differences, we can drop any terms proportional to $\onev$ in $\eta^w(s)$.

@@

The first of these equations is solved by
%
\begin{equation}\label{eq:detagensol}
  \delta\eta_i = B\alpha^{i-1} + C\alpha^{1-i},
  \qquad\text{where}\qquad
  \alpha^2 - 2(s+1)\alpha + 1 = 0,
\end{equation}
%
with $B$ and $C$ determined by the boundary conditions provided by the last two equations of \eqref{eq:detahalf}:
%
\begin{equation}\label{eq:unicoeffs}
  B = -\frac{2\alpha}{(1+\alpha)(\alpha^{\frac{M}{2}}+\alpha^{-\frac{M}{2}})s},
  \qquad
  C = -\frac{2}{(1+\alpha)(\alpha^{\frac{M}{2}}+\alpha^{-\frac{M}{2}})s}.
\end{equation}
%
This can be used to compute the Laplace transform
%
\begin{equation}\label{eq:unilaplace}
  A(s) = \frac{2\eta^w_1(s)}{M}
   = \frac{2}{M}\prn{\frac{1}{s}+B+C}
   = \frac{2(\alpha^{\frac{M}{2}}-1)^2}{Ms(\alpha^M+1)}.
\end{equation}
%

@@

The following elements of $\enc$ and $\eq$ are differ from \eqref{eq:unienc}:
%
\begin{equation}\label{eq:stickyenc}
  \begin{aligned}
  \enc_{12} = -\enc_{MM-1} &= \frac{\varepsilon}{2},
  &\qquad
  \eq_1 = \eq_M &= \frac{1}{2+(M-2)\varepsilon},
  \\ &&
  \eq_i &=  \frac{\varepsilon}{2+(M-2)\varepsilon}
  \quad\text{for}\quad 1<i<M.
  \end{aligned}
\end{equation}
%
This means that the Laplace transform is given by
%
\begin{equation}\label{eq:stickyareaeta}
  \hat{A}(s) = \frac{\varepsilon(\eta^w_1(s)-\eta^w_M(s))}{2+(M-2)\varepsilon}
       = \frac{2\varepsilon\, \eta^w_1(s)}{2+(M-2)\varepsilon}.
\end{equation}
%

The $\eta^w_i(s)$ take the same general form \eqref{eq:detagensol}, but with different coefficients due to the different boundary conditions
%
\begin{equation}\label{eq:detabndsticky}
\begin{aligned}
  \frac{\varepsilon\delta\eta_2}{2} - \prn{s+\frac{\varepsilon}{2}}\delta\eta_1 &= 0, \\
  \frac{\delta\eta_{\frac{M}{2}-1}}{2} - \prn{s+\frac{3}{2}}\delta\eta_{\frac{M}{2}} &= \frac{1}{s}.
\end{aligned}
\end{equation}
%
These are solved by
%
\begin{equation}\label{eq:stickycoeffs}
\begin{aligned}
  B &= -\frac{ 2 \alpha^{\frac{M}{2}} (\alpha-(1-\varepsilon)) }{ (1+\alpha) [(1+\alpha^{M}) - (1-\varepsilon) \alpha (1+\alpha^{M-2}) ]s}, \\
  C &= -\frac{ 2 \alpha^{\frac{M}{2}} (1-(1-\varepsilon)\alpha) }{ (1+\alpha) [(1+\alpha^{M}) - (1-\varepsilon) \alpha (1+\alpha^{M-2}) ]s},
\end{aligned}
\end{equation}
%
which leads to the Laplace transform
%
\begin{equation}\label{eq:stickylaplace}
  \hat{A}(s) = \frac{2\varepsilon}{[2+(M-2)\varepsilon]s} \,
      \frac{ (\alpha^{\frac{M}{2}}-1)^2 - (1-\varepsilon)\alpha(\alpha^{\frac{M-2}{2}}-1)^2 }{ (\alpha^M + 1) - (1-\varepsilon)\alpha(\alpha^{M-2}+1) }.
\end{equation}
%

@@

The following elements of $\enc$ and $\eq$ are differ from \eqref{eq:unienc}:
The following elements of $\enc$ and $\eq$ are differ from \eqref{eq:unienc}:
%
\begin{equation}\label{eq:shortenenc}
  \begin{aligned}
  \enc_{M-1M} = -\enc_{21} &= \frac{\varepsilon}{2},
  &\qquad
  \eq_1 = \eq_M &= \frac{\varepsilon}{M-2(1-\varepsilon)},
  \\ &&
  \eq_i &=  \frac{1}{M-2(1-\varepsilon)}
  \quad\text{for}\quad 1<i<M.
  \end{aligned}
\end{equation}
%
This means that the Laplace transform is given by
%
\begin{equation}\label{eq:shortenareaeta}
  \hat{A}(s) = \frac{\varepsilon(\eta^w_1(s)-\eta^w_M(s)) + (1-\varepsilon)(\eta^w_2(s)-\eta^w_{M-2}(s))}{M-2(1-\varepsilon)}
       = \frac{2\varepsilon\, \eta^w_1(s) + 2(1-\varepsilon)\eta^w_2(s)}{M-2(1-\varepsilon)}.
\end{equation}
%

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thb}{\boldsymbol{\theta}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{ideal}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}

@@

Using the exact same proof as in the case $s=0$, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptb_{ij}(s)\eq_j
\end{equation}
%
is independent of the starting state $i$, but now $\eta(s) = \tr\fund(s) - \frac{\tau}{1+s\tau}$.
We can the define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptb_{ij}(s)\eq_j \prn{\frac{1\pm\w_j}{2}} =  \sum_{j\in\pm} \fptb_{ij}(s)\eq_j.
\end{equation}
%
We can arrange the states in order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \etw_i(s) = \sum_j \fptb_{ij}(s)\eq_j \w_j
    = \eta^+_i(s) - \eta^-_i(s) =2\eta^+_i(s) - \eta(s) =\eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing $\etw_i(s)$ is the same as the order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
These quantities can still be used when $\w$ takes more than two values.

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurvehom} (ignoring the denominator)
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) \\
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }{ \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s - r\frg}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \enc_{ij} (\etw_{i}(s) - \etw_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

In analogy with the case $s=0$, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    c_k(s) &= \sum_{ij} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \\
    a_i(s) &= \sum_j \eq_i \enc_{ij} (\etw_{i}(s) - \etw_{j}(s)),\\
    \implies
    \hat{A}(s) &= \sum_k c_k(s) \eq_k \w_k
      = \sum_i a_i(s).
  \end{aligned}
\end{equation}
%

@@

Using the same approach as the area bound in \cite{Lahiri2013synapse}, and defining $\thb_i(s) = \sum_j \fptb_{ij}(0) a_j(s)$,  we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
  \pdiff{\hat{A}(s)}{\M\potdep_{mn}}
     = f\potdep \eq_m \prn{ r \brk{\thb_m(s) - \thb_n(s)}
     +\prn{rc_m(s) \pm 1} \brk{\etw_m(s) - \etw_n(s)} },
\end{equation}
%
with the upper/lower sign in $\pm$ corresponding to derivatives \wrt $\M\potdep$.
The term with $\Theta(s)$ comes from differentiating $\eq$, the term with $c(s)$ comes from differentiating $\etw(s)$ and the term with $\pm1$ comes from differentiating $\enc$ in \eqref{eq:larea}.

To write down the Hessian, we will first define some notation.
Given a four-index array $H_{ijkl}$, we define $H\trans_{ijkl} = H_{klij}$
Then we denote
%
\begin{equation}\label{eq:hessparts}
\begin{aligned}
  R_{ijkl} &= 
    &&\eq_i \brc{\fund_{ik}(0) - \fund_{jk}(0)} \brc{\thb_k(s) - \thb_l(s)} \\
    &&&+ \eq_i \brc{[\fund(0)\enc\fund(s)]_{ik} - [\fund(0)\enc\fund(s)]_{jk}} \brc{\etw_k(s) - \etw_l(s)} \\
    &&&+ \eq_i c_i(s) \brc{\fund_{ik}(s) - \fund_{jk}(s)} \brc{\etw_k(s) - \etw_l(s)},  \\
  S_{ijkl} &= 
    &&\eq_i \brc{\fund_{ik}(0) - \fund_{jk}(0)} \brc{\etw_k(s) - \etw_l(s)} \\
    &&&+ \eq_k \brc{\fund_{ki}(s) - \fund_{li}(s)} \brc{\etw_i(s) - \etw_j(s)}.
\end{aligned}
\end{equation}
%
Then we can write the hessian as
%
\begin{equation}\label{eq:hessian}
\begin{aligned}
  \pdiff{^2\hat{A}(s)}{\M\pot_{ij} \partial\M\pot_{kl}} &=
     (f\pot)^2 (R_{ijkl} + R\trans_{ijkl})
     + f\pot(S_{ijkl} + S\trans_{ijkl}), \\
  \pdiff{^2\hat{A}(s)}{\M\pot_{ij} \partial\M\dep_{kl}} &=
     f\pot f\dep (R_{ijkl} + R\trans_{ijkl})
     - f\pot S_{ijkl} + f\dep S\trans_{ijkl}, \\
  \pdiff{^2\hat{A}(s)}{\M\dep_{ij} \partial\M\pot_{kl}} &=
     f\pot f\dep (R_{ijkl} + R\trans_{ijkl})
     - f\pot S\trans_{ijkl} + f\dep S_{ijkl}, \\
  \pdiff{^2\hat{A}(s)}{\M\pot_{ij} \partial\M\pot_{kl}} &=
     (f\dep)^2 (R_{ijkl} + R\trans_{ijkl})
     - f\dep(S_{ijkl} + S\trans_{ijkl}), \\
\end{aligned}
\end{equation}
%
This is useful in numerical maximisation.

@@

Now we'll maximise $\snrb(\tau)$ for some fixed $\tau$, subject to the constraints \eqref{eq:constr}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding $\eq\w$ fixed.
We can maximise the ration \wrt $\eq\w$ later.
Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eq_i \enc_{ij} (\etw_i(s) - \etw_j(s))
        +\sum_{i j} \prn{ f\pot\mu\pot_{ij} \M\pot_{ij} + f\dep\mu\dep_{ij} \M\dep_{ij} }\\
        &+ \lambda \prn{ \Delta\pr - \sum_i \eq_i\w_i },
\end{aligned}
\end{equation}
%
where $\Delta\pr$ is the constant value we are holding $\eq\w$ at.
After maximising
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\M\potdep_{ij}} = 0, \quad
  \mu\potdep_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu\potdep_{ij}} \geq 0, \quad
  \mu\potdep_{ij}\pdiff{\CL}{\mu\potdep_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
The derivatives, for $m \neq n$ are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{f\potdep} \pdiff{\CL}{\Mh\potdep_{mn}} =& \,
      \eq_m \prn{ r \brk{\thb_m(s) - \thb_n(s)}
     +\prn{rc_m(s) \pm 1} \brk{\etw_m(s) - \etw_n(s)} } \\
     &+ \mu\potdep_{mn} -  \mu\potdep_{mm}
     + \lambda \eq_m \sum_i (\fptb_{mi}(0)-\fptb_{ni}(0)) \eq_i\w_i.
\end{aligned}
\end{equation}
%
These have the same form as for $s=0$, which allowed us to argue that the model with maximal area must have the serial topology, \cite{Leibold2008serial,Ben-DayanRubin2007sparse}.

@@

Here we will look at the model in \autoref{fig:heuristicmodels}\ref{fig:serial_uniform}.
Looking at \eqref{eq:larea}, the only thing we need is differences in $\etw_i(s)$.
In fact, given that the only nonzero elements of $\enc$ are
%
\begin{equation}\label{eq:unienc}
  \enc_{ii+1}=\frac{1}{2} \quad\text{for}\quad i<M,
  \qquad
  \enc_{ii-1}=-\frac{1}{2} \quad\text{for}\quad i>1,
\end{equation}
%
and $\eq_i = \frac{1}{M}$, we have
%
\begin{equation}\label{eq:uniareaeta}
  \hat{A}(s) = \frac{\etw_1(s) - \etw_M(s)}{M}.
\end{equation}
%

Note that
%
\begin{equation}\label{eq:etafund}
  \etw(s) = \text{const.} - \fund(s)\w.
\end{equation}
%
As we are only interested in differences of the $\etw_i(s)$, we can drop the constant.
Then
%
\begin{equation}\label{eq:etarecur}
  -(s\I + \onev\pib - \frg)\etw(s) = \w.
\end{equation}
%
We can then write
%
\begin{equation}\label{eq:detarecur}
  \etw(s) = -\frac{(\pib\etw(s))\onev+\w}{s} + \delta\eta(s),
  \qquad
  (\frg-s\I)\delta\eta(s) = \frac{\frg\w}{s}.
\end{equation}
%
As we are only interested in differences, we can drop any terms proportional to $\onev$ in $\etw(s)$.

@@

The first of these equations is solved by
%
\begin{equation}\label{eq:detagensol}
  \delta\eta_i = B\alpha^{i-1} + C\alpha^{1-i},
  \qquad\text{where}\qquad
  \alpha^2 - 2(s+1)\alpha + 1 = 0,
\end{equation}
%
with $B$ and $C$ determined by the boundary conditions provided by the last two equations of \eqref{eq:detahalf}:
%
\begin{equation}\label{eq:unicoeffs}
  B = -\frac{2\alpha}{(1+\alpha)(\alpha^{\frac{M}{2}}+\alpha^{-\frac{M}{2}})s},
  \qquad
  C = -\frac{2}{(1+\alpha)(\alpha^{\frac{M}{2}}+\alpha^{-\frac{M}{2}})s}.
\end{equation}
%
This can be used to compute the Laplace transform
%
\begin{equation}\label{eq:unilaplace}
  A(s) = \frac{2\etw_1(s)}{M}
   = \frac{2}{M}\prn{\frac{1}{s}+B+C}
   = \frac{2(\alpha^{\frac{M}{2}}-1)^2}{Ms(\alpha^M+1)}.
\end{equation}
%

@@

The following elements of $\enc$ and $\eq$ are differ from \eqref{eq:unienc}:
%
\begin{equation}\label{eq:stickyenc}
  \begin{aligned}
  \enc_{12} = -\enc_{MM-1} &= \frac{\varepsilon}{2},
  &\qquad
  \eq_1 = \eq_M &= \frac{1}{2+(M-2)\varepsilon},
  \\ &&
  \eq_i &=  \frac{\varepsilon}{2+(M-2)\varepsilon}
  \quad\text{for}\quad 1<i<M.
  \end{aligned}
\end{equation}
%
This means that the Laplace transform is given by
%
\begin{equation}\label{eq:stickyareaeta}
  \hat{A}(s) = \frac{\varepsilon(\etw_1(s)-\etw_M(s))}{2+(M-2)\varepsilon}
       = \frac{2\varepsilon\, \etw_1(s)}{2+(M-2)\varepsilon}.
\end{equation}
%

The $\etw_i(s)$ take the same general form \eqref{eq:detagensol}, but with different coefficients due to the different boundary conditions
%
\begin{equation}\label{eq:detabndsticky}
\begin{aligned}
  \frac{\varepsilon\delta\eta_2}{2} - \prn{s+\frac{\varepsilon}{2}}\delta\eta_1 &= 0, \\
  \frac{\delta\eta_{\frac{M}{2}-1}}{2} - \prn{s+\frac{3}{2}}\delta\eta_{\frac{M}{2}} &= \frac{1}{s}.
\end{aligned}
\end{equation}
%
These are solved by
%
\begin{equation}\label{eq:stickycoeffs}
\begin{aligned}
  B &= -\frac{ 2 \alpha^{\frac{M}{2}} (\alpha-(1-\varepsilon)) }{ (1+\alpha) [(1+\alpha^{M}) - (1-\varepsilon) \alpha (1+\alpha^{M-2}) ]s}, \\
  C &= -\frac{ 2 \alpha^{\frac{M}{2}} (1-(1-\varepsilon)\alpha) }{ (1+\alpha) [(1+\alpha^{M}) - (1-\varepsilon) \alpha (1+\alpha^{M-2}) ]s},
\end{aligned}
\end{equation}
%
which leads to the Laplace transform
%
\begin{equation}\label{eq:stickylaplace}
  \hat{A}(s) = \frac{2\varepsilon}{[2+(M-2)\varepsilon]s} \,
      \frac{ (\alpha^{\frac{M}{2}}-1)^2 - (1-\varepsilon)\alpha(\alpha^{\frac{M-2}{2}}-1)^2 }{ (\alpha^M + 1) - (1-\varepsilon)\alpha(\alpha^{M-2}+1) }.
\end{equation}
%

@@

The following elements of $\enc$ and $\eq$ are differ from \eqref{eq:unienc}:
The following elements of $\enc$ and $\eq$ are differ from \eqref{eq:unienc}:
%
\begin{equation}\label{eq:shortenenc}
  \begin{aligned}
  \enc_{M-1M} = -\enc_{21} &= \frac{\varepsilon}{2},
  &\qquad
  \eq_1 = \eq_M &= \frac{\varepsilon}{M-2(1-\varepsilon)},
  \\ &&
  \eq_i &=  \frac{1}{M-2(1-\varepsilon)}
  \quad\text{for}\quad 1<i<M.
  \end{aligned}
\end{equation}
%
This means that the Laplace transform is given by
%
\begin{equation}\label{eq:shortenareaeta}
  \hat{A}(s) = \frac{\varepsilon(\etw_1(s)-\etw_M(s)) + (1-\varepsilon)(\etw_2(s)-\etw_{M-2}(s))}{M-2(1-\varepsilon)}
       = \frac{2\varepsilon\, \etw_1(s) + 2(1-\varepsilon)\etw_2(s)}{M-2(1-\varepsilon)}.
\end{equation}
%
